abxD01 Paper

### 2015-03-12 PAPER.Rmd
Update statistical methods

***Statistical Analysis & Modeling*** All analyses were conducted using R version 3.1.2. Complete analysis scripts are available at the online repository for this study (https://github.com/SchlossLab/Schubert_AbxD01_mBio_2015).

Need text about...
* correlation analysis
* comparison of titration levels
* For the random forest you use 1% within each treatment group, for the correlation you state using 0.1 and 0.01% across all samples. Need to stay consistent.
* statistical methods used to differentiate the abundances of OTUs in the titrations

Random forest regression models were constructed using the randomForest R package using XX,000 trees [ref]. The model was constructed using the relative abundance of those OTUs that had an average relative abundance within any antibiotic treatment group of 1%. This resulted in 44 OTUs. The regression was performed using the log10 transformation of the number of CFU per gram of fecal material as the dependent variable.

>>>>

***Statistical Analysis & Modeling*** All analyses were conducted using R version 3.1.2. OTUs were considered for analysis if their average relative abundance within any treatment group was at least 1% (43 OTUs). Spearman rank correlation analysis was performed with a Benjamini and Hochberg adjustment between OTU counts or diversity levels and *C. difficile* CFU/g feces. Comparison of bacterial levels among titration groups or delayed groups of the same antibiotic was performed using the Kruskall-Wallis rank sum test followed by pairwise Wilcoxon rank sum tests with a Benjamini and Hochberg adjustment. Comparison of log10 transformed *C. difficile* CFU/g feces between experimental groups was calculated using ANOVA and subsequently pairwise T tests with a Benjamini and Hochberg adjustment. Random forest regression models were constructed using the randomForest R package using 5,000 trees [ref]. The regression was performed using the log10 transformation of the number of CFU/g fecal material as the dependent variable and the 43 OTUs as predictor variables. Complete analysis scripts are available at the online repository for this study (https://github.com/SchlossLab/Schubert_AbxD01_mBio_2015).
